A Sound and Complete Deep Embedding of Arbitrary Normal Modal Logics in Coq

### 2025-08-20 paper/COLA/paper.tex
Some rephrasing; clarifications

In this section, we describe our formalization of the completeness result for the
Hilbert proof system with respect to the Kripke semantics.
Before we start,
it is worth mentioning that there are different notions of completeness, and
the literature is not always clear about the difference of those~\cite{Popkorn_1994,modal_lean}.
%-------------------------------------------------------------------------------
The semantic entailment, $\Gamma\models\varphi$, represents a global consequence since, by our definition,
we expect that the hypotheses are valid in every world in a model instead
of having $\varphi$ hold only on those worlds where the hypotheses are valid \cite{de1999global}.
Also, the completeness result may be
weak, which is only valid without hypotheses, or strong, allowing it to be stated with any set of
hypotheses \cite{blackburn}. We follow the definitions as established by Popkorn \cite{Popkorn_1994}
and note that we prove a weak completeness result using a global consequence, which subsumes a local one (as local consequence implies global consequence
\cite{de1999global}). A strong completeness proof, as of now, is left as future work.
It's worth noting that our completeness theorem is, in the words of
Popkorn, \emph{rather weak} \cite[p. 119-120]{Popkorn_1994}; the result is applicable to any
possible sets of axioms extending System K. Other
notions of completeness, argueable more expressive, will relate sets of axioms
to respective sets of model frames (cf. Section \ref{sec:correspondence}). Still, the present result provides a basis
for most such stronger completeness theorems.

>>>>

In this section, we describe our formalization of the completeness result for the
Hilbert proof system with respect to the Kripke semantics.
Before we start,
it is worth mentioning that there are different notions of completeness, and
the literature is not always clear about the difference of those~\cite{Popkorn_1994,modal_lean}.
%-------------------------------------------------------------------------------
The semantic entailment, $\Gamma\models\varphi$, represents a global consequence since, by our definition,
we expect that the hypotheses are valid in every world in a model instead
of having $\varphi$ hold only on those worlds where the hypotheses are valid \cite{de1999global}.

Also, the completeness result may be
weak, which is only valid without hypotheses, or strong, allowing it to be stated with any set of
hypotheses \cite{blackburn}. We follow the definitions as established by Popkorn \cite{Popkorn_1994}
and note that we prove a weak completeness result using a global consequence, which subsumes a local one (as local consequence implies global consequence
\cite{de1999global}). A strong completeness proof, as of now, is left as future work, as such result may be carried as an extension of the present one \cite{Popkorn_1994}.
It's worth noting that our completeness theorem is, in the words of
Popkorn, \emph{rather weak} \cite[p. 119-120]{Popkorn_1994}; the result is applicable to any
possible sets of axioms extending System K. Other
notions of completeness, considered more expressive, will relate sets of axioms
to respective sets of model frames (cf. Section \ref{sec:correspondence}). Still, the present result provides a basis
for most such stronger completeness theorems.
